---
title: "AssetClassAnalysisPt2_PersonalFinance"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(lubridate)
library(readr)
library(janitor)
library(here)
library(haven)
library(tigris)
library(tidycensus)
library(purrr)
library(ipumsr)
library(data.table)
library(stringr)
library(httr2)
library(jsonlite)
library(dplyr)
library(slider)
library(broom)
library(survey)
library(srvyr)
library(marginaleffects)
```


```{r Step 0: Pull in ANES Data, include=TRUE}
anes_panel <- read_dta(here("00_rawdata", "ANES_Data", "anes_timeseries_cdf_stata_20260205.dta"))
```

```{r Step 1: Cleaning Up the Dataset, include=TRUE}
# Check the variables
anes_panel <- anes_panel %>%
  rename(year = VCF0004, trust_gov_index = VCF0656, trust_gov = VCF0604, econ_views = VCF0870, stock_owns = VCF9224, social_class = VCF0149, person_finances = VCF0880, person_finances_scale = VCF0880a, personal_finances_next = VCF0881, age = VCF0101, age_group = VCF0102, gender = VCF0104, race = VCF0105a, educ = VCF0110, income_group = VCF0114, emp_status = VCF0116, homeowner = VCF0146, marital_stat = VCF0147, partisan_id = VCF0301, partisan_strength = VCF0305, pol_interest = VCF0310, union_mem = VCF0127)

#Turn Dataset into Survey Object
anes_svy <- anes_panel %>%
  filter(year >= 2000) %>%
  as_survey_design(
    ids = 1,
    weights = VCF0009z
  ) 

anes_svy