---
title: "Precarity Scratch Writing"
date: today 
filters: 
  - include-code-files
  - wordcount
format:
  pdf: 
    word-count: "{{wordcount}}"
    number-sections: false
author:
  - name: Christian Hosam
    email: ch128@wellesley.edu
    affiliation: 
      - name: Wellesley College
        city: Wellesley
        state: MA
        url: www.christianhosam.com
keywords:
  - Race
  - Black Politics
  - Congress
  - Representation
  - American Political Economy

project: 
  execute-dir: project
---

```{r setup, include = FALSE}
# set global options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = FALSE)
# Set the working directory to be the project directory (aka root or top-level directory)
knitr::opts_knit$set(root.dir = here:: here())
```

```{r Package Import, include=FALSE}
library(here)
library(knitr)
library(devtools)
library(tidyverse)
library(rticles)
library(bookdown)
library(kableExtra)
library(ggthemes)
library(stargazer)
library(pander)
```

Neoliberalism isn't dying, it's withering on the vine. But with unprecedented levels of inequality, the rise of the far-right, and the ongoing climate crisis, it is clear that neoliberalism is not working for the majority of people. The question is, what comes next?

1.  The Racial Construction of Recessions

2.  The Politics of the Precariat

3.  When Am I Going to make a Living? Young People Finding Careers in a New Economic Regime

4.  "People of Color" Under Precarity? The Economic Realities of a Label

5.  Gendered Work, Gendered Precarity

6.  The Long Death of Neoliberalism
